%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Jianshuang Wang} % Your name
\address{+8615298368071} % Your phone number
\address{http://xeostream.github.com \\ iostreamin@gmail.com} % Your website and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Southeast University, NanJing} \hfill {\em August 2010 - present} \\ 
B.S. in Software Engineering, Merit Student of Southeast University 
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{iQQ Chat System}{August 2011 - September 2011}{Backgroud Developer}{Southeast University, NJ}
\item The System is based on Java Socket.User can communicate with each other, send or receive files .
\item The System use Mysql database store user information and chat history.
\item My role in my team is database development and files transfer function development.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Email Client}{December 2011 - January 2012}{Test Developer}{Southeast University, NJ}
\item The Email client use smtp and pop3 protocol to realize sending and receiving Email.
\item My job is to compile unit test and pack the software client.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{imusic Online Music Website}{August 2012 - september 2012}{Algorithm Designer \& Developer}{Southeast University, NJ}
\item Filter song by some options such as type,singer and so on.Users can listen songs which they choose when they are online.
\item Search data by Web Crawler and get useful song's information by analysing xml files.
\item Development Frame is SSH,Development tool is netbeans,Page effects is realized by JQuery and AJAX.
\item My job in my team is to design sing choosing algorithm and backgroud developer.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Moses Machine Translate System}{July 2013}{Developer}{NJ}
\item Based on Moses Machine Translate System and translate English into other language
\item Train model, Adjust parameter, Statistical translation result
\item Basic knowledge about Machine Learning
\end{rSubsection}

\end{rSection}
%-------------------------------------------------

\begin{rSection}{Internship}

\begin{rSubsection}{baozoumanhua(baozoumanhua.com)}{september 2012 - july 2013}{Software Developer}{NanJing}
\item Ruby On Rails
\end{rSubsection}

\begin{rSubsection}{trendmicro}{july 2013 - present}{Web Developer}{NanJing}
\item Python, Django
\item CMS, Statistical Machine Translation
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Major Courses & Artificial Intelligence-90, OOP(Java)-93, Probability Theory-92 \\
Computer Languages & Java = Python $>$ Ruby = C $>$ C++ = SQL = HTML \\
Protocols \& APIs & XML $>$ JSON \\
Databases & MySQL $>$ MongoDB \\
Tools & git,hg,netbeans,ecplise,3ds max\\
English & Basic English language reading and writing, CET4-521, CET6-459
%Pattern & Test Driven Development
\end{tabular}

\end{rSection}

\begin{rSection}{Self Evaluation}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Hard working and positive. \\
Devoted to Test Driven Development and open source \\
Desired to software development
\end{tabular}

\end{rSection}
%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
